% =============================================================================
% modules/deployment.tex — Craftalism Deployment
% =============================================================================


\chapter{Craftalism Deployment}
\label{ch:deployment}

\modulelang{Docker Compose · PostgreSQL 18 · Nginx}

\textcolor{CraftGray}{\textit{Container orchestration — single-command deployment for the full platform}}

\bigskip

\section{Overview}

The Deployment repository contains the Docker Compose configuration and environment templates needed to run the entire Craftalism platform. It contains no application source code; all services are pulled from pre-built images published to the GitHub Container Registry. The current baseline entrypoint is the \code{./prod} workflow, which refreshes pinned image digests, prepares the production environment, and starts the stack in the correct dependency order.

\section{Responsibilities}

\begin{itemize}
  \item Defines the full service topology and inter-service networking in \code{docker-compose.yml}.
  \item Manages a one-shot database initializer that creates the \code{authserver} database before the Authorization Server starts.
  \item Downloads and installs the Craftalism Economy plugin JAR into the Minecraft server container at startup using the configured \code{ECONOMY\_VERSION}.
  \item Templates an \code{env.example} file covering all required and optional configuration for the full stack.
  \item Exposes the platform through the deployment edge with HTTPS and dashboard access control in the production baseline.
\end{itemize}

\section{Architecture and Design}

\subsection{Service Topology}

\rowcolors{2}{CraftLight}{white}
\begin{tabularx}{\linewidth}{@{} L{4.6cm} L{4.0cm} X @{}}
  \toprule
  {\tableheadstyle Container} & {\tableheadstyle Image} & {\tableheadstyle Purpose} \\
  \midrule
  \code{craftalism-postgres}    & \code{postgres:18-alpine}                    & Primary database for API and Authorization Server. \\
  \code{auth-db-init}           & \code{postgres:18-alpine}                    & One-shot; creates \code{authserver} DB then exits. \\
  \code{craftalism-auth-server} & \code{ghcr.io/.../authorization-server}      & OAuth2 token issuer. \\
  \code{craftalism-api}         & \code{ghcr.io/.../craftalism-api}            & Core REST API. \\
  \code{craftalism-dashboard}   & \code{ghcr.io/.../craftalism-dashboard}      & Admin web UI. \\
  \code{craftalism-minecraft}   & \code{itzg/minecraft-server}                 & Paper game server + economy plugin. \\
  \bottomrule
\end{tabularx}

\subsection{Startup Dependency Order}

\begin{enumerate}
  \item \code{craftalism-postgres} starts and passes its health check.
  \item \code{auth-db-init} runs and creates the \code{authserver} database, then exits.
  \item \code{craftalism-auth-server} and \code{craftalism-api} start in parallel (both depend on a healthy PostgreSQL).
  \item \code{craftalism-dashboard} and \code{craftalism-minecraft} start once the API is healthy.
\end{enumerate}

\subsection{Port Mapping}

\rowcolors{2}{CraftLight}{white}
\begin{tabularx}{\linewidth}{@{} L{5.2cm} C{2.4cm} X @{}}
  \toprule
  {\tableheadstyle Service} & {\tableheadstyle Host Port} & {\tableheadstyle Notes} \\
  \midrule
  Dashboard           & 443 / 80  & HTTPS at the deployment edge; proxied to the internal dashboard service. \\
  Craftalism API      & Internal  & Reached through the edge or internal network wiring. \\
  Authorization Server & 443 / 80 & HTTPS at the deployment edge for externally reachable issuer traffic. \\
  Minecraft           & 25565 & Game traffic (TCP/UDP). \\
  RCON                & 25575 & Remote console. \\
  \bottomrule
\end{tabularx}

\section{Tech Stack}

\rowcolors{2}{CraftLight}{white}
\begin{tabularx}{\linewidth}{@{} L{3.0cm} L{5.2cm} X @{}}
  \toprule
  {\tableheadstyle Category} &
  {\tableheadstyle Technology} &
  {\tableheadstyle Notes} \\
  \midrule
  Orchestration & Docker Compose v2          & \\
  Database      & PostgreSQL 18 (alpine)     & Shared instance; separate databases per service \\
  Game Server   & \code{itzg/minecraft-server} & Paper-compatible; plugin auto-downloaded \\
  Networking    & Docker bridge network      & All services on \code{craftalism-network} \\
  \bottomrule
\end{tabularx}

\section{Configuration}

\rowcolors{2}{CraftLight}{white}
\begin{tabularx}{\linewidth}{@{} L{4.8cm} L{2.0cm} C{1.6cm} X @{}}
  \toprule
  {\tableheadstyle Variable} &
  {\tableheadstyle Default} &
  {\tableheadstyle Required} &
  {\tableheadstyle Description} \\
  \midrule
  \code{DB\_PASSWORD}              & ---  & \textbf{Yes} & PostgreSQL password for the \code{craftalism} user. \\
  \code{MINECRAFT\_CLIENT\_SECRET} & ---  & \textbf{Yes} & OAuth2 client secret; must match the Authorization Server. \\
  \code{RSA\_PRIVATE\_KEY}         & ---  & \textbf{Yes} & PEM RSA private key with literal \code{\textbackslash n} separators. \\
  \code{RSA\_PUBLIC\_KEY}          & ---  & \textbf{Yes} & PEM RSA public key with literal \code{\textbackslash n} separators. \\
  \code{AUTH\_ISSUER\_URI}         & ---  & \textbf{Yes} & Externally reachable URL of the Authorization Server. Must be identical across all services. \\
  \code{ECONOMY\_VERSION}          & ---  & \textbf{Yes} & GitHub Release tag of the economy plugin JAR to download on Minecraft container startup. \\
  \bottomrule
\end{tabularx}

\note{See Appendix~\ref{app:shared-env} for variables that must be consistent across multiple services, particularly \code{AUTH\_ISSUER\_URI} and \code{MINECRAFT\_CLIENT\_SECRET}.}

\section{Known Limitations}

\begin{itemize}
  \item No \code{generate-keys.sh} script exists despite being referenced in \code{env.example}. RSA keys must be generated manually.
  \item Final release confidence still depends on running the deployment smoke flow against the exact intended release SHAs or tags.
\end{itemize}

\section{Roadmap}

\begin{itemize}
  \item Add a \code{generate-keys.sh} script for RSA key pair generation and formatting.
  \item Add a generated operator evidence pack that records image digests, health checks, and smoke results after successful deployments.
  \item Add broader failure-path and recovery verification beyond the current baseline smoke flow.
\end{itemize}
